Paper 2, Econ 980x

### 2022-12-09 Paper2.Rmd
commit

#leisure hours aggregate
csv %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  labs(
  title = "Distribution of annual individual leisure hours",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~year) +
  labs(
  title = "Distribution of annual individual leisure hours",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

#leisure hours aggregate by gender
csv %>%
  group_by(gender) %>%
  ggplot(mapping = aes(x = bls_leis) )+
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender) +
    labs(
  title = "Distribution of annual individual leisure hours by gender",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender + year) +
  labs(
  title = "Distribution of annual individual leisure hours by gender",
  x = "Annual Hours",
  y = "Count",
  caption = "Data from ATUS",
)

# Median
csv %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# Median 
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# Mean
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = mean_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Mean annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# All Quantile
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
    facet_wrap(~ gender) +
  labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

@@

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
  facet_wrap(~gender) +
    labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(median = median(bls_leis)) %>%
  clean_names() %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = median)) +
  geom_line() +
  facet_wrap(~gender) +
      labs(
  title = "Annual individual leisure hours by gender",
  y = "Annual Hours",
  x = "Year",
  caption = "Data from ATUS",
)

@@

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(year) %>%
  count(emp) %>%
  filter(emp == "Unemployed") %>%
  ggplot(mapping = aes(x = year, y = n)) +
  geom_line() +
  labs(
  title = "Unemployment",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)
  #facet_wrap(~emp)

@@

newcsv1 %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Annual individual leisure hours",
  y = "Annual Hours",
  x = "Count",
  caption = "Data from ATUS",
)

>>>>

#leisure hours aggregate
csv %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~year) +
  labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

#leisure hours aggregate by gender
csv %>%
  group_by(gender) %>%
  ggplot(mapping = aes(x = bls_leis) )+
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender) +
    labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

csv %>%
  filter(year %in% c(2007, 2009)) %>%
  ggplot(mapping = aes(x = bls_leis)) +
  geom_histogram(binwidth=50) +
  facet_wrap(~ gender + year) +
  labs(
  title = "Distribution of daily individual leisure minutes",
  x = "Daily Minutes",
  y = "Count",
  caption = "Data from ATUS",
)

# Median
csv %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Median 
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(median(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = median_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Median daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# Mean
csv %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  group_by(year, gender) %>%
  summarize(mean(bls_leis)) %>%
  clean_names() %>%
  ggplot(aes(x = year, y = mean_bls_leis)) +
  geom_line() +
  facet_wrap(~ gender) +
  labs(
  title = "Mean daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# All Quantile
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
    facet_wrap(~ gender) +
  labs(
  title = "Daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

@@

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(quantile_25 = quantile(bls_leis, 0.25), quantile_50 = quantile(bls_leis, 0.5), quantile_75 = quantile(bls_leis, 0.75)) %>%
  clean_names() %>%
  pivot_longer(quantile_25:quantile_75, names_to = "quantile", values_to = "hours") %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = hours, group = quantile, colour = quantile)) +
  geom_line() +
  facet_wrap(~gender) +
    labs(
  title = "Daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

# by year, gender
csv %>%
  group_by(year, gender) %>%
  summarize(median = median(bls_leis)) %>%
  clean_names() %>%
  filter(year > 2005) %>%
  filter(year < 2011) %>%
  ggplot(aes(x = year, y = median)) +
  geom_line() +
  facet_wrap(~gender) +
      labs(
  title = "Daily individual leisure minutes by gender",
  y = "Daily Minutes",
  x = "Year",
  caption = "Data from ATUS",
)

@@

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(year) %>%
  count(emp) %>%
  filter(emp == "Unemployed") %>%
  ggplot(mapping = aes(x = year, y = n)) +
  geom_line() +
  labs(
  title = "Unemployment",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)
  #facet_wrap(~emp)

@@

newcsv1 %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)

newcsv1 %>%
  filter(year > 2006) %>%
  filter(year < 2011) %>%
  group_by(emp, gender, new_educ, year) %>%
  summarize(median = median(bls_leis)) %>%
  ggplot(mapping = aes(x = year, y = median, group = new_educ, colour = new_educ)) +
  geom_line() +
  facet_wrap(~gender + emp) +
  labs(
  title = "Daily individual leisure minutes",
  y = "Daily Minutes",
  x = "Count",
  caption = "Data from ATUS",
)
